---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# momaz

<!-- badges: start -->
<!-- badges: end -->

**Consensus gene ranking from multi-omic association studies using Fisher, SSz, and cwMCD**

## Installation

You can install the development version of momaz from [GitHub](https://github.com/doraaobodo/momaz) with:

``` r
# install.packages("remotes")
remotes::install_github("doraaobodo/momaz")
```
## Description
The \code{momaz} package implements and compares three statistical approaches for consolidating significance rankings from multi-omic association studies into consensus gene rankings:

- **Fisher’s method**  
- **Sum of squared z-statistics (SSz)**  
- **Cellwise Minimum Covariance Determinant (cellMCD)**  

The package includes functions to compute diagnostics, evaluate method performance in simulations, and generate visualizations such as bivariate scatterplots, uniform QQ plots, and ranked heatmaps.
## How to Use:

This is a basic example which shows you how to solve a common problem:

```{r example}
library(momaz)
# Example data (toy matrix)
set.seed(123)
X <- matrix(rnorm(100*5), nrow = 100, ncol = 5)

# Run cwMCD
res <- cwMCD(X)

# Bivariate plot for first two variables
plot_bivariate_cwMCD(res, vars = c("input.clm_1", "input.clm_2"))

# QQ plot of p-values
qq_uniform(res)

# Heatmap of top rows by method
heatmap_cwMCD(res, methods = c("MCD","Fisher","SSz"), top_n = 25)
```

